Nondeterministic Bigraphical Reactive Systems for Markov Decision Processes\thanks{Supported by organization x.}

### 2018-08-12 paper.tex
TikZ illustrations to the rescue!

\documentclass[runningheads]{llncs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{color}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{wasysym}
\usepackage[lighttt]{lmodern}
\usepackage{siunitx}
\usepackage{hyperref}
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
 \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{document}
\title{Nondeterministic Bigraphical Reactive Systems for Markov Decision
  Processes\thanks{Supported by organization x.}}
\titlerunning{Nondeterministic BRSs for MDPs}
\author{Paulius Dilkas}
\authorrunning{P. Dilkas}
\institute{University of Glasgow, Glasgow, UK}
\maketitle

@@

@@

The room is a $2 \times 2$ grid of \texttt{Cell}s, which is generated when the
\texttt{Agent} gets to a \texttt{Cell} with an empty \texttt{Node} (represented
by \texttt{Node\{n\}.1})\footnote{Multiple different rooms can be implemented by
having each previously empty \texttt{Node} contain a node of different control.
This way a different probability distribution (with different possible outcomes)
can be assigned to each room.}. In order for the room to be generated before any
other action can take place, the two reaction rules in Listing~\ref{agent2_room}
are put on a higher priority class. With probability $p$, the generated room has
each \texttt{Cell} linked to its two neighbours; and with probability $1-p$, the
top two \texttt{Cell}s are not linked, possibly forcing the agent to choose a
different path. Finally, we have four actions, each with a single reaction rule
with probability $1$, corresponding to the four possible directions of travel.
The reaction rules are very similar to those of our previous example, an example
of which can be found in Listing~\ref{agent2_north}.

@@

BIG TODO!

>>>>

\documentclass[runningheads]{llncs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{color}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{wasysym}
\usepackage[lighttt]{lmodern}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{phaistos}

\renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{document}

\title{Nondeterministic Bigraphical Reactive Systems for Markov Decision
  Processes\thanks{Supported by organization x.}}
\titlerunning{Nondeterministic BRSs for MDPs}
\author{Paulius Dilkas}
\authorrunning{P. Dilkas}
\institute{University of Glasgow, Glasgow, UK}
\maketitle

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    % walls
    \draw (3, 2) -- (3, 0) -- (1, 0) -- (1, 2) -- (0, 2) -- (0, 3) -- (3, 3) -- (3, 2) -- (2, 2);
    \draw[brown,ultra thick] (1, 2) -- (2, 2);
    % the door
    \draw[red,ultra thick,dashed] (2, 2) -- (2, 1);
    % the background grid
    \draw[gray,very thin] (1, 3) -- (1, 2);
    \draw[gray,very thin] (2, 3) -- (2, 2);
    \draw[gray,very thin] (1, 1) -- (3, 1);
    \draw[gray,very thin] (2, 1) -- (2, 0);
    % the agent
    \node at (0.5, 2.3) {\PHchild};
  \end{tikzpicture}
  \caption{The full map. The agent is in the top left cell. There is a thick
    brown door connecting the middle cell of the top row with a $2 \times 2$
    room below. The red dashed wall exists with probability $1-p$.}
  \label{agent2_map}
\end{figure}

@@

The room is a $2 \times 2$ grid of \texttt{Cell}s, which is generated when the
\texttt{Agent} gets to a \texttt{Cell} with an empty \texttt{Node} (represented
by \texttt{Node\{n\}.1})\footnote{Multiple different rooms can be implemented by
having each previously empty \texttt{Node} contain a node of different control.
This way a different probability distribution (with different possible outcomes)
can be assigned to each room.}. In order for the room to be generated before any
other action can take place, the two reaction rules in Listing~\ref{agent2_room}
are put on a higher priority class. With probability $p$, the generated room has
each \texttt{Cell} linked to its two neighbours; and with probability $1-p$, the
top two \texttt{Cell}s are not linked, possibly forcing the agent to choose a
different path (see Fig. \ref{agent2_map}). Finally, we have four actions, each
with a single reaction rule with probability $1$, corresponding to the four
possible directions of travel. The reaction rules are very similar to those of
our previous example, an example of which can be found in
Listing~\ref{agent2_north}.

@@
